Comments on Blair and Sambanis, 2020, \"Forecasting Civil Wars: Theory and Structure in an Age of 'Big Data' and Machine Learning\", *JCR*

### 2020-05-04 issues.Rmd
Small changes to issues, remade the table 1 csv to include all of the 6 mon mods, and moved my table 1 replication
investigate table 4

library(readr)
library(dplyr)
```

@@

Before listing the primary issues we identified, we should note that we are partial to their approach. Theory is important. It is helpful for forecasting problems, especially with regards to identifying which variables to include in a model. This is particularly true when the goal is to assess how ...

@@

@@

>>>>

library(readr)
library(dplyr)
library(kableExtra)
```

@@

Before listing the primary issues we identified, we should note that we are partial to their approach. Theory is important. It is helpful for forecasting problems, especially with regards to identifying which variables to include in a model. This is particularly true when the goal is to assess how ... (RM: I want to add something here about identifying potential policy interventions that can help advert onset...)

@@

<!-- \input{data/replicated-table-1.tex} -->

@@

<!-- 
AB: going to put some detailed technical notes in here.

The 2016 forecasts are created in R and contained in pred_escalation_6mo_inc_civil_ns.
That data frame actually has predictions for 2008 to 2016.

The data from which all this is created has the following values for the plus1 and non-lead DV:

  incidence_civil_ns_plus1     n
                     <dbl> <int>
1                        0  4581
2                        1    20
3                       NA   483

  incidence_civil_ns     n
               <dbl> <int>
1                  0  4562
2                  1    20
3                 NA   502

Looking at the pattern of missing values, it is fairly clear that the incidence variables were originally incidence, but changed to onset such that the first value in a sequence of 1's remained a 1 while the rest were set to NA. Like:

c(0, 1, 1, 1, 0) becomes (c(0, 1, NA, NA, 0))

And it is also fairly clear that "incidence_civil_ns_plus1" is a 1-period lead indicator for the outcome that one can use as a prediction target insteaad of having to lag all inputs.

Anyways, in R training, "incidence_civil_ns_plus1" is used as the target for the models. It has 20 positive values for data ranging from 2001 to 2016.

The predictions, including 2016 forecasts, are written to disk and then Stata picks up. The crucial coding for Table 4 is in `6mo_make_confusion_matrix.do`.

Two strange things happen there.

Sub-issue 1: First, the forecasts are assessed with "incidence_civil_ns", not "incidence_civil_ns_plus1". Based on the DV names, I would imagine that "plus1" is a lead version, so the actual predictions for 2016-H1 are contained in the predicted value for "incidence_civil_ns_plus1" in 2015-H2, since the plus 1 puts the time period to 2016-H1.

(It could be that the 2016-H1 data in "data/6mo_data_OOS.dta" are just a copy of 2015-H2, in which case ok. I haven't checked.)

This is a relatively minor point.

Sub-issue 2: The second issue, and this is key, is that missing values in "incidence_civil_ns" are recoded to 1 in `6mo_make_confusion_matrix.do` line 52. This is what does all the heavy lifting in Table 4. Otherwise there are no 1 values in the data:

  incidence_civil_ns     n
  <chr>              <int>
1 0                    149
2 NA                    15

So it appears that the variable is essentially changed back from the onset coding in which ongonig conflicts are NA, back to incidence coding.

-->
